Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-11-23 src/tex/ms.tex
Change document class
Change document class to REVTeX 4.2

% \documentclass[aps,prd,twocolumn,superscriptaddress,preprintnumbers,floatfix,nofootinbib]{revtex4-2}
\documentclass[reprint,amsmath,amssymb,aps,twocolumn]{aastex631}

@@

@@

% Previous studies
Previous studies have constrained amplitude birefringence by performing Bayesian inference.
In \citet{Maria_2021}, they considered the distribution of observed inclination of the GW events in GWTC-2, the second GW transient catalog, and use the distribution to constrain the amplitude birefringence effect with the assumption of frequency independence in GW amplitude birefringence.
In \citet{Yamada_2020} and \citet{Wang_2021}, they both modeled the waveform under birefringence effect with a simplify assumption and performed Bayesian inference on the events in GWTC-1, the first GW transient catalog.

@@

For some previous studies on the birefringence property such as \citet{Maria_2021}, they assume the effect of birefringence is independent of the frequency, which is a zeroth-order approximation of the birefringence model in Chern-Simons gravity.
This would create a degeneracy between $\kappa$ and $\iota$, as they can affect the amplitude ratio in the same way.
To reconstruct the amplitude ratio from the interferometer data, an $\iota$ representing a more face-off inspiral can pair with a positive $\kappa$, or an $\iota$ representing a more face-on inspiral with a negative $\kappa$.
As a result, many pairs of $\iota$ and $\kappa$ can be plausible with the frequency independence.

@@

% Comparison with previous studies
In \citet{Maria_2021}, the authors gave a constraint on GW amplitude birefringence by performing statistical analysis on GWTC-2.
We convert the constraint to the same format as ours to make comparison.
They were able to constrain $\kappa$ to be $|\kappa| \lesssim 0.74$ at $1 \sigma$.
We were able to obtain a tighter constraint on $\kappa$ with $|\kappa| \lesssim 0.04$ at $1 \sigma$.
This is a order of magnitude improvement in constraining $\kappa$.
This is due to the fact that we have much more events from GWTC-3 compared to GWTC-2.

>>>>

\documentclass[aps,prd,twocolumn,superscriptaddress,preprintnumbers,floatfix,nofootinbib]{revtex4-2}

@@

\maketitle

@@

% Previous studies
Previous studies have constrained amplitude birefringence by performing Bayesian inference.
In \citet{Okounkova_2022}, they considered the distribution of observed inclination of the GW events in GWTC-2, the second GW transient catalog, and use the distribution to constrain the amplitude birefringence effect with the assumption of frequency independence in GW amplitude birefringence.
In \citet{Yamada_2020} and \citet{Wang_2021}, they both modeled the waveform under birefringence effect with a simplify assumption and performed Bayesian inference on the events in GWTC-1, the first GW transient catalog.

@@

For some previous studies on the birefringence property such as \citet{Okounkova_2022}, they assume the effect of birefringence is independent of the frequency, which is a zeroth-order approximation of the birefringence model in Chern-Simons gravity.
This would create a degeneracy between $\kappa$ and $\iota$, as they can affect the amplitude ratio in the same way.
To reconstruct the amplitude ratio from the interferometer data, an $\iota$ representing a more face-off inspiral can pair with a positive $\kappa$, or an $\iota$ representing a more face-on inspiral with a negative $\kappa$.
As a result, many pairs of $\iota$ and $\kappa$ can be plausible with the frequency independence.

@@

% Comparison with previous studies
In \citet{Okounkova_2022}, the authors gave a constraint on GW amplitude birefringence by performing statistical analysis on GWTC-2.
We convert the constraint to the same format as ours to make comparison.
They were able to constrain $\kappa$ to be $|\kappa| \lesssim 0.74$ at $1 \sigma$.
We were able to obtain a tighter constraint on $\kappa$ with $|\kappa| \lesssim 0.04$ at $1 \sigma$.
This is a order of magnitude improvement in constraining $\kappa$.
This is due to the fact that we have much more events from GWTC-3 compared to GWTC-2.
